---
title: "Perception Action Analysis"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
setwd("~/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM")

pacman::p_load(tidyverse,dplyr, data.table, vroom, ggplot2, readbulk, lme4, rstanarm, MuMIn, lmerTest, lme4,multcomp, interactions, sjPlot, sjmisc)


```

Read data
```{r}
df <- read_bulk(directory = "/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/logfiles_emma/",
    fun = read_csv)

df <- read_csv("/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/logfiles_emma/logfile_test_2021_Dec_13_0937_1.csv")
```

Remove the weird [' '] part of the Colourtask (key press), leaving only the letter
```{r}

df$Colourtask = gsub("'", "", df$Colourtask)
df$Colourtask = gsub("\\[|\\]", "", df$Colourtask)
unique(df$Colourtask)
```

Making stimulus variable neat (only leaving y1a format)
```{r}
df$Stimulus = gsub("/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/stimuli/", "", df$Stimulus)
df$Stimulus = gsub(".png", "", df$Stimulus)
```

Make a simple stim variable
```{r}

# df$Stimulus = gsub("a", "", df$Stimulus)
df$Stimulus = gsub("b", "", df$Stimulus)
df$Stimulus = gsub("1234567890", "", df$Stimulus)

length(unique(df$Stimulus))
which(df$Stimulus %in% "y")

```

Do a subset test
```{r}

test <- df %>%
    filter(ID == "sjovtparticipantid")

```


Create correct variable. If variable 'Stimulus' contains character value y, the variable "correct" should be 
```{r}

df$correct = ifelse((df$Stimulus %in% "y" & df$Colourtask == "y") | (df$Stimulus %in% "r" & df$Colourtask == "r"),1,0)

```

Create crossmodal correspondence variable?
```{r}
# 1 is yellow
# 2 is red
# 0 is control

df$crossmodal = ifelse((df$Stimulus %in% "y" & df$Condition == 1) | (df$Stimulus %in% "r" & df$Condition == 2), 1,0)

```

```{r}
hist(df$ReactionTime)

```

```{r}
hist(df$Stimulus)
```

## Analysis 
https://www.crumplab.com/statisticsLab/lab-9-repeated-measures-anova.html

Independent variable: Stimulus, Condition
Dependent: RT, correct

Find mean RT for each condition
```{r}

```


